---
title: "R Notebook"
output: html_notebook
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = T, results = "hide")
library(knitr)
library(rlang)
library(tidyverse)
library(readxl)
library(docxtools)
library(data.table)
library(dplyr)
library(purrr)
library(tidyr)
library(lubridate) 
library(ggplot2)
library(scales)
library(gridExtra)
library(ggthemes)
library(viridis)
library(knitr)
library(reshape2)
library(ggQC)
library(kableExtra)
library(tibble)
library(colorspace)
library(RPostgreSQL)
library(DescTools)
```


```{r}
library(DBI)

db <- 'calculation'  #provide the name of your db

host_db <- 'localhost' #i.e. 

db_port <- '5432'  # or any other port specified by the DBA

db_user <- 'yuyue'  

db_password <- '136818'

con <- dbConnect(RPostgres::Postgres(), dbname = db, host=host_db, port=db_port, user=db_user, password=db_password)
```

```{r}
dbWriteTable(con, "chem_comptox25022021", chem_comptox)
```

```{r}
dbWriteTable(con, "calculation_countryis", calculation_countryis)
```

read all tables
```{r}
files <- list.files(pattern = "*.xlsx", full.names = TRUE)
file_name <- list.files(pattern = "*.xlsx")

readexcel <- function(x, y){
  #browser()
  x <- read_excel(x)
  y <- gsub(".xlsx", "", y)
  assign(y, x, envir = .GlobalEnv)
}

map2(files, file_name, readexcel)
```


give ids to input_bayer from connections to the `def` tables
*should add checking steps like checking NAs(things that do not occur in our dataset but provided by Bayer)*
```{r}
input_id <- input_bayer %>%
  left_join(def_country, by = "name_country") %>%
  select(-c(description_country, remarks_country, description_bayer, remarks_bayer))

input_id <- input_id %>%
  left_join(def_crop, by = "name_crop") %>%
  select(-c(description_crop, remarks_crop, scientificname_crop))
  
input_id <- input_id %>%
  left_join(def_cropstage, by = "name_cropstage") %>%
  select(-c(description_cropstage, remarks_cropstage))

def_bbch <- def_bbch %>%
  select(code_bbch, description_bbch, remarks_bbch) %>%
  distinct(.) %>%
  mutate(id_bbch = row_number()) %>%
  select(id_bbch, code_bbch, description_bbch, remarks_bbch)

input_id <- input_id %>%
  left_join(def_bbch, by = "code_bbch") %>%
  select(-c(description_bbch, remarks_bbch))

input_id <- input_id %>%
  left_join(def_chemical, by = "casrn_chemical") %>%
  select(-c(description_chemical, remarks_chemical))

input_id <- input_id %>%
  left_join(def_app, by = "name_app") %>%
  select(-c(description_app, remarks_app))
```

```{r}
input_idna <- input_id %>%
  filter(is.na(id_chemical))
```


combine ids with association tables

*if put names in, duplicate, create multiple names*
```{r}
assn_crop_cropclass1 <- assn_crop_cropclass %>%
  select(-name_crop)
assn_id <- input_id %>%
  left_join(assn_crop_cropclass1, by = "id_crop")

assn_app_refapp1 <- assn_app_refapp %>%
  select(id_app_refapp, id_app, id_refapp)
assn_id <- assn_id %>%
  left_join(assn_app_refapp1, by = "id_app")

assn_cropclass_refapp_appdrift1 <- assn_cropclass_refapp_appdrift %>% #remember crop height
  select(id_cropclass_refapp_appdrift, id_refapp, id_cropclass, id_appdrift, `height<50cm`)
assn_cropclass_refapp_appdrift1 <- assn_cropclass_refapp_appdrift1 %>%
  filter(`height<50cm` == "T")
assn_id <- merge(assn_id, assn_cropclass_refapp_appdrift1, by = c("id_refapp", "id_cropclass"), all.x = TRUE)

```

```{r}
summary(assn_id)
```



input tables join
```{r}
input_cropintercept1 <- input_cropintercept %>%
  select(id_inputci, id_crop_cropstage, id_crop, id_cropstage, code_bbch, `ci_m^2/m^2`)
join_ci <- assn_id %>%
  left_join(input_cropintercept1, by = c("id_crop", "id_cropstage")) %>%
  mutate(`ci_m^2/m^2` = as.numeric(`ci_m^2/m^2`))
na_ci <- join_ci %>%
  filter(is.na(`ci_m^2/m^2`))

input_pestcheck <- input_pestlci %>%
  mutate(ci_diff = `ci_m^2/m^2_1` - round(`ci_m^2/m^2_1`, 2))

input_pestlci1 <- input_pestlci %>%
  select(id_pestlci, id_appdrift_ci, id_appdrift, `ci_m^2/m^2`, `c_primair_[kg/kg]`, `c_primsoil_[kg/kg]`, `c_primcrop_[kg/kg]`, `c_primofffield_[kg/kg]`) 
join_pestlci <- join_ci %>%
  left_join(input_pestlci1, by = c("id_appdrift", "ci_m^2/m^2"))

join_pestlcicheck <- join_pestlci %>%
  filter(is.na(id_pestlci))

input_offfield1 <- input_offfield %>%
  select(id_offfield, id_country, `frac_agr.soil_[m^3/m^3]`, `frac_nat.soil_[m^3/m^3]`, `frac_water_[m^3/m^3]`)
join_offfield <- join_pestlci %>%
  left_join(input_offfield1, by = "id_country")

input_usetox1 <- input_usetox %>%
  select(id_usetox, id_chemical, casrn_chemical, `cf_air_[PAF m^3d/kg]`, `cf_water_[PAF m^3d/kg]`, `cf_soiln_[PAF m^3d/kg]`, `cf_soila_[PAF m^3d/kg]`)
join_usetox <- join_offfield %>%
  left_join(input_usetox1, by = "casrn_chemical")
```




```{r}
summary(join_pestlci)
```


```{r}
summary(join_usetox)
```



calculating impact scores
```{r}
calculation <- join_usetox %>%
  mutate(`applied_dose_[kg/ha]` = case_when(is.na(`treated_area_[1000ha/yr]`) ~ NA_real_,
                                  `treated_area_[1000ha/yr]` == 0 ~ 0,
                                  TRUE ~ `applied_mass_[1000kg/yr]`/`treated_area_[1000ha/yr]`))
```

is
```{r}
calculation_is <- calculation %>%
  mutate(`is_air_[PAFm^3d/kg]` = `c_primair_[kg/kg]` * `cf_air_[PAF m^3d/kg]`) %>%
  mutate(`is_nat.soil_offField_[PAFm^3d/kg]` = `c_primofffield_[kg/kg]` * `frac_nat.soil_[m^3/m^3]` * `cf_soiln_[PAF m^3d/kg]`) %>%
  mutate(`is_water_offField_[PAFm^3d/kg]` = `c_primofffield_[kg/kg]` * `frac_water_[m^3/m^3]` * `cf_water_[PAF m^3d/kg]`) %>%
  #field soil and off-field soil together
  mutate(`is_agr.soil_[PAFm^3d/kg]` = `c_primsoil_[kg/kg]` * `cf_soila_[PAF m^3d/kg]` + `c_primofffield_[kg/kg]` * `frac_agr.soil_[m^3/m^3]` * `cf_soila_[PAF m^3d/kg]`) %>%
  #field soil and off-field soil separate
  mutate(`is_agr.soil_field_[PAFm^3d/kg]` = `c_primsoil_[kg/kg]` * `cf_soila_[PAF m^3d/kg]`) %>%
  mutate(`is_agr.soil_offField_[PAFm^3d/kg]` = `c_primofffield_[kg/kg]` * `frac_agr.soil_[m^3/m^3]` * `cf_soila_[PAF m^3d/kg]`)
```

unit_is
```{r}
calculation_unitis <- calculation_is %>%
  mutate(`is_air_[PAFm^3d/ha]` = `is_air_[PAFm^3d/kg]` * `applied_dose_[kg/ha]`) %>%
  mutate(`is_nat.soil_offField_[PAFm^3d/ha]` = `is_nat.soil_offField_[PAFm^3d/kg]` * `applied_dose_[kg/ha]`) %>%
  mutate(`is_water_offField_[PAFm^3d/ha]` = `is_water_offField_[PAFm^3d/kg]` * `applied_dose_[kg/ha]`) %>%
  # field soil and off-field soil together
  mutate(`is_agr.soil_[PAFm^3d/ha]` = `is_agr.soil_[PAFm^3d/kg]` * `applied_dose_[kg/ha]`) %>%
  # field soil and off-field soil separate
  mutate(`is_agr.soil_field_[PAFm^3d/ha]` = `is_agr.soil_field_[PAFm^3d/kg]` * `applied_dose_[kg/ha]`) %>%
  mutate(`is_agr.soil_offField_[PAFm^3d/ha]` = `is_agr.soil_offField_[PAFm^3d/kg]` * `applied_dose_[kg/ha]`)
```

Annual country-level freshwater impacts
```{r}
calculation_countryis <- calculation_unitis %>%
  mutate(`is_air_[PAFm^3d/country/yr]` = `is_air_[PAFm^3d/ha]` * `treated_area_[1000ha/yr]` * 1000) %>%
  mutate(`is_nat.soil_offField_[PAFm^3d/country/yr]` = `is_nat.soil_offField_[PAFm^3d/ha]` * `treated_area_[1000ha/yr]` * 1000) %>%
  mutate(`is_water_offField_[PAFm^3d/country/yr]` = `is_water_offField_[PAFm^3d/ha]` * `treated_area_[1000ha/yr]` * 1000) %>%
  # field soil and off-field soil together
  mutate(`is_agr.soil_[PAFm^3d/country/yr]` = `is_agr.soil_[PAFm^3d/ha]` * `treated_area_[1000ha/yr]` * 1000) %>%
  # field soil and off-field soil separate
  mutate(`is_agr.soil_field_[PAFm^3d/country/yr]` = `is_agr.soil_field_[PAFm^3d/ha]` * `treated_area_[1000ha/yr]` * 1000) %>%
  mutate(`is_agr.soil_offField_[PAFm^3d/country/yr]` = `is_agr.soil_offField_[PAFm^3d/ha]` * `treated_area_[1000ha/yr]` * 1000)
```

```{r}
summary(calculation_countryis)
```


```{r}
countryis_na <- calculation_countryis %>%
  filter(is.na(`is_agr.soil_[PAFm^3d/country/yr]`))
```

write table to database
```{r}
dbWriteTable(con, "calculation_210307", calculation_countryis)
```

---

bbch
```{r}
bbch_bayer <- calculation_countryis %>%
  select(code_bbch.x, name_crop, name_cropclass, name_cropstage, `ci_m^2/m^2`, code_bbch.y, name_country) %>%
  unique()
```

```{r}
write.csv(calculation_countryis, file = "calculation_countryis.csv")
```

```{r}
appliedmass_NA <- calculation_countryis %>%
  filter(`applied_mass_[1000kg/yr]` == 0)
treatedarea_NA <- calculation_countryis %>%
  filter(`treated_area_[1000ha/yr]` == 0)
```

```{r}
crops_bayer <- calculation_countryis %>%
  filter(name_crop == "BRASSICAS")
```


