---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(readxl)
library(purrr)
library(ggthemes)
library(dplyr)
library(ggplot2)
```


```{r}
files <- list.files('C:/me/data gaps/20220824xgboost/', 
                        pattern = ".csv$", recursive = TRUE, full.names = TRUE)
    
chem_full_xgb <- read_csv(files) %>% bind_rows()
```


```{r}
chem.list <- unique(chem_full_xgb$casrn_chemical)
chem <- chem.list[1]
exist.dat_country <- exist.dat %>%
  left_join(join_short_uni, by = c(c("score", "name_crop_earthstat" = "variable", "layer_climate"))) %>%
  filter(!is.na(name_country))
  group_by(name_country) %>%
  summarize(count = n_distinct(casrn_chemical))

exist.dat.chem <- exist.dat %>%
  #filter(casrn_chemical == chem) %>%
  select(name_crop_earthstat, name_region.y, name_group_yy, HDI, landevap, layer_climate, climate_main, climate_sub, score, wd, casrn_chemical) %>%
  mutate(group = "ori")
chem_full_xgb_pred <- chem_full_xgb %>%
  #filter(casrn_chemical == chem) %>%
  mutate(wd = 10^pred.xgb) %>%
  select(name_crop_earthstat, name_region.y, name_group_yy, HDI, landevap, layer_climate, climate_main, climate_sub, score, wd, casrn_chemical) %>%
  mutate(group = "pred")
chem_dose <- rbind(exist.dat.chem, chem_full_xgb_pred)
for(i in 1:57){
  chem_dose %>%
  filter(casrn_chemical %in% chem.list[(5*i-4):(5*i)]) %>%
  filter(!is.na(name_region.y)) %>%  #check region NA scenarios
  ggplot(aes(x = name_crop_earthstat, y = wd)) +
  geom_boxplot(size = 1,
               outlier.shape = NA,
               #outlier.color = "black",
               #outlier.size = 1,
               aes(fill = group)) +
  geom_jitter(alpha = 0.5, width = 0.2, aes(color = name_region.y), size = 1) +
  theme_minimal() +
  facet_wrap(~ casrn_chemical, scales = "free_x", nrow = 1) +
  #geom_smooth(method=lm, formula = formula, se=FALSE, fullrange=TRUE) +
  scale_color_brewer(palette="Paired")+
  coord_flip()
ggsave(paste0("20220823chem_dose_pred_ori", i, ".jpeg"), width = 40, height = 20, units = "cm")
}
chem_dose %>%
  filter(casrn_chemical %in% chem.list[5]) %>%
  #filter(casrn_chemical == "1071-83-6") %>%
  filter(!is.na(name_region.y)) %>%  #check region NA scenarios
  ggplot(aes(x = name_crop_earthstat, y = wd)) +
  geom_boxplot(size = 1,
               outlier.shape = NA,
               #outlier.color = "black",
               #outlier.size = 1,
               aes(fill = group)) +
  geom_jitter(alpha = 0.5, width = 0.2, aes(color = name_region.y), size = 1) +
  theme_minimal() +
  facet_wrap(~ casrn_chemical, scales = "free_x", nrow = 1) +
  #geom_smooth(method=lm, formula = formula, se=FALSE, fullrange=TRUE) +
  scale_color_brewer(palette="Paired")+
  coord_flip()
ggsave("20220818chem_dose_pred_ori_101007-96-1.jpeg", width = 40, height = 20, units = "cm")
```

```{r}
write.csv(join_short_uni_ratio_r, "20220830join_short_uni_ratio_r.csv")
join_short_uni_ratio_r <- read.csv("20220830join_short_uni_ratio_r.csv")
join_short_uni_ratio_r <- join_short_uni_ratio %>%
  #mutate(score = round(as.numeric(score), 13)) %>%
  mutate(name_country = case_when(name_cntr == "The Former Yugoslav Republic O" ~ "Macedonia, the former Yugoslav Republic of",
                                  name_cntr == "Republic Of Korea" ~ "Korea (the Republic of)",
                                  name_cntr == "Iran, Islamic Republic of" ~ "Iran (Islamic Republic of)",
                                  name_cntr == "United Republic Of Tanzania" ~ "Tanzania, the United Republic of",
                                  name_cntr == "U.k. Of Great Britain And Nort" ~ "United Kingdom",
                                  name_cntr == "United States Of America" ~"United States of America",
                                  name_cntr == "Republic Of Moldova" ~ "Moldova (the Republic of)",
                                  TRUE ~ name_cntr)) 
chem_dose_r <- chem_dose %>%
  mutate(score = round(as.numeric(score),13))
write.csv(chem_dose, "20220908chem_dose.csv")
chem_dose <- read.csv("20220908chem_dose.csv")
write.csv(join_short_uni_ratio_r, "20220908join_short_uni_ratio_r.csv")
join_short_uni_ratio_r <- read.csv("20220908join_short_uni_ratio_r.csv")
country_chemlist_other <- chem_dose %>%
  left_join(join_short_uni_ratio_r, by = c("score", "name_crop_earthstat" = "variable"))

#check scenarios cannot find country
country_chemlist_other_na <- country_chemlist_other %>%
  filter(is.na(layer_climate.x))

#check country pesticide count
country_chemlist_other_count <- country_chemlist_other %>%
  group_by(name_country, group) %>%
  summarize(predictgroupcount = n_distinct(group), chemicalcount = n_distinct(casrn_chemical), predict = list(unique(group))) %>%
  left_join(no.country.continent, by = c("name_country" = "name_country"))
country_chemlist_other_count %>%
  group_by(name_country) %>%
  summarize(duplicate = n()) %>%
  filter(duplicate > 1)

country_chemlist_other_count %>%
  filter(!is.na(name_country)) %>%
  filter(name_country != "Nigeria") %>%
  filter(!is.na(name_region)) %>%
  ggplot(aes(x = name_country, y = chemicalcount)) +
  geom_bar(aes(fill = group), stat='identity') +
  facet_wrap(~name_region, scales = "free_x") +
  scale_x_discrete(guide = guide_axis(angle = 90))
ggsave("20220909country_chemlist_count.jpeg", width = 12, height = 8)

country_chemlist_other_countcrop <- country_chemlist_other %>%
  group_by(name_country, group, name_group_yy) %>%
  summarize(predictgroupcount = n_distinct(group), chemicalcount = n_distinct(casrn_chemical), predict = list(unique(group))) %>%
  left_join(no.country.continent, by = c("name_country" = "name_country"))

country_chemlist_other_countcrop %>%
  filter(!is.na(name_country)) %>%
  filter(name_country != "Nigeria") %>%
  filter(!is.na(name_region)) %>%
  filter(name_region == "South America") %>%
  ggplot(aes(x = name_country, y = chemicalcount)) +
  geom_bar(aes(fill = group), stat='identity') +
  facet_wrap(~name_group_yy) +
  scale_x_discrete(guide = guide_axis(angle = 90))
ggsave("20220909country_chemlist_countsouthamerica.jpeg", width = 60, height = 30, units = "cm")

#check countries predicted nothing
country_chemlist_no <- no.country.continent %>%
  filter(!name_country%in%country_chemlist_other_count$name_country)

croparea_country <- join_short_country_uni_ratio %>%
  group_by(name_cntr) %>%
  summarize(sumcroparea = sum(cropsumarea)) %>%
  mutate(name_country = case_when(name_cntr == "The Former Yugoslav Republic O" ~ "Macedonia, the former Yugoslav Republic of",
                                  name_cntr == "Republic Of Korea" ~ "Korea (the Republic of)",
                                  name_cntr == "Iran, Islamic Republic of" ~ "Iran (Islamic Republic of)",
                                  name_cntr == "United Republic Of Tanzania" ~ "Tanzania, the United Republic of",
                                  name_cntr == "U.k. Of Great Britain And Nort" ~ "United Kingdom",
                                  name_cntr == "United States Of America" ~"United States of America",
                                  name_cntr == "Republic Of Moldova" ~ "Moldova (the Republic of)",
                                  TRUE ~ name_cntr)) %>%
  left_join(no.country.continent, by = c("name_country" = "name_country"))
```


```{r}
input_appbbch_atrazine <- input_appbbch %>%
  filter(casrn_chemical == "1071-83-6") %>%
  group_by(name_country, name_crop_earthstat, bbch_specific) %>%
  summarize(mindose = min(dose), maxdose = max(dose)) %>%
  mutate(ratiomaxmin = maxdose/mindose)

input_appbbch_us <- input_cas %>%
  group_by(name_country) %>%
  summarize(count = n_distinct(casrn_chemical))
```


```{r}
input_appbbch_bbch_yes %>%
  group_by(bbch_specific) %>%
  summarize(massbbchgroup = sum(applied_mass_kkg), countbbchgroup = n()) %>%
  ggplot(aes(x = bbch_specific, y = massbbchgroup)) +
  geom_col()
```
#input with application method bbch seed
```{r}
#from multiple parameter determine seed/soil/crop
input_appbbch_exist <- input_appbbch %>%
  filter(bbch_YN == "YES") %>%
  filter(application_YN == "YES") %>%
  mutate(treatmentori = case_when(name_stagegroup == "00 SEED-DRESSING" ~ "seed",
                                  name_stagegroup == "0 SOIL" ~ "soil",
                                  #name_refapp == "Seed treatment" ~ "seed",
                                  name_indication == "SEED-DRESSING" ~ "seed",
                                  #name_refapp == "Soil incorporation" ~ "soil",
                                  name_cropstage == "0000-SEED-DRESSING" ~ "seed",
                                  TRUE ~ "crop"))

input_appbbch_exist %>%
  group_by(name_activeindication, treatmentori) %>%
  summarize(count = n(), summass = sum(applied_mass_kkg)) %>%
  ggplot(., aes(x = name_activeindication, y = treatmentori, fill = log10(summass))) +
  geom_tile() +
  scale_fill_viridis(discrete=FALSE, direction = -1)
#from individual indicator determine seed/soil/crop, compared with reference application method
input_appbbch_exist <- input_appbbch %>%
  filter(bbch_YN == "YES") %>%
  filter(application_YN == "YES") #%>%
  filter(name_indication == "SEED-DRESSING")
  
input_appbbch_exist %>%
  group_by(name_activeindication, name_refapp) %>%
  summarize(count = n(), summass = sum(applied_mass_kkg)) %>%
  ggplot(., aes(x = name_activeindication, y = name_refapp, fill = log10(summass))) +
  geom_tile() +
  scale_fill_viridis(discrete=FALSE, direction = -1)

#input seed with indication
```

#input with indication-active
```{r}
indication_active <- input_appbbch %>%
  group_by(casrn_chemical, name_ai) %>%
  summarize(active_indication =  list(unique(name_activeindication)), activeindicationcount = n_distinct(name_activeindication),indicationcount = n_distinct(name_indication))

table
casrncheck <- input_appbbch %>%
  group_by(name_ai, casrn_chemical, name_ai_bayer, casrn_chemical_bayer) %>%
  summarize(count = n()) %>%
  mutate(casmatch = case_when(casrn_chemical_bayer == casrn_chemical ~ "match",
                              TRUE ~ "unmatch")) %>%
  filter(casmatch == "unmatch")

indication_active_group <- input_appbbch %>%
  group_by(name_activeindication) %>%
  summarize(countchem = n_distinct(casrn_chemical))
indication_group <- input_appbbch %>%
  group_by(name_indication) %>%
  summarize(countchem = n_distinct(casrn_chemical))
indication_activeor_group <- input_appbbch %>%
  group_by(name_activeindication, name_indication) %>%
  summarize(countchem = n_distinct(casrn_chemical))

indication_activeor_group %>%
  ggplot(., aes(x = name_activeindication, y = name_indication, fill = countchem)) +
  geom_tile() +
  scale_fill_viridis(discrete=FALSE, direction = -1)
```
#herbicides application methods
```{r}
input_appbbch_herbi <- input_appbbch %>%
  #filter(name_activeindication == "HERBICIDES-ACTIV") %>%
  group_by(name_app, name_refapp, name_activeindication) %>%
  summarize(count = n())
```

#seed dressing related application methods
```{r}
input_appbbch_seeddressing <- input_appbbch %>%
  filter(name_stagegroup == "00 SEED-DRESSING"  | name_indication == "SEED-DRESSING" |
                                  name_cropstage == "0000-SEED-DRESSING") %>%
  group_by(name_app, name_refapp, name_stagegroup, name_indication, name_cropstage, name_activeindication) %>%
  summarize(count = n())
input_appbbch_seeddressingall <- input_appbbch %>%
  group_by(name_app, name_refapp, name_stagegroup, name_indication, name_cropstage, name_activeindication) %>%
  summarize(count = n())
```


```{r}
input_appbbch_combination <- input_appbbch %>%
  group_by(name_country, name_crop_earthstat, casrn_chemical, application_YN, bbch_YN) %>%
  summarize(count = n())
```

```{r}
input_crop <- input_caschem %>%
  group_by(name_crop_earthstat) %>%
  summarize(summass = sum(applied_mass_kkg))
```


#calibration ccc level xgboost dose prediction, without separation of treatment
```{r}
files <- list.files('C:/me/data gaps/20220912xgboost_calibration/', 
                        pattern = ".csv$", recursive = TRUE, full.names = TRUE)
    
chem_pred_xgb <- read_csv(files) %>% bind_rows()
```

#chemical existence for rest countries
```{r}
no.dat.cpp.exist.full.country <- no.dat.cpp.pred.exist.full %>%
  left_join(join_short_uni_ratio_r, by = c("score", "name_crop_earthstat" = "variable"))
no.dat.cpp.country <- no.dat.cpp.exist.full.country %>%
  group_by(name_country, name_region.y) %>%
  summarize(chemcount = n_distinct(casrn_chemical))
```

#result with first two steps predict existence and doses, ccc level xgboost dose prediction, without separation of treatment
```{r}
files <- list.files('C:/me/data gaps/20220929xgboost_usa/', 
                        pattern = ".csv$", recursive = TRUE, full.names = TRUE)
    
chem_full_xgb <- read_csv(files) %>% bind_rows()

chem_full_xgb_a <- chem_full_xgb %>%
  left_join(join_short_uni, by = c("HDI", "landevap", "score", "name_crop_earthstat" = "variable"))

n_distinct(chem_full_xgb$casrn_chemical)

chem_full_xgb_ccc <- chem_full_xgb_a %>%
  group_by(name_country, name_crop_earthstat, casrn_chemical) %>%
  summarize(count = n())

chem_dose_atrazine <- chem_full_xgb_a %>%
  filter(casrn_chemical == "1912-24-9") %>%
  mutate(dose = 10^(pred.xgb)) %>%
  group_by(name_country, name_crop_earthstat) %>%
  summarize(dose_avg = mean(dose, na.rm = TRUE))

chem_full_xgb_luxembourrg <- chem_full_xgb_a %>%
  filter(name_country == "Luxembourg")

```


```{r}
chem.list <- unique(chem_full_xgb$casrn_chemical)
chem <- chem.list[1]
exist.dat_country <- exist.dat %>%
  left_join(join_short_uni_ratio, by = c(c("score", "name_crop_earthstat" = "variable", "layer_climate"))) %>%
  filter(!is.na(name_cntr)) %>%
  mutate(mass = 10^logwd * cropsumarea) %>%
  group_by(name_cntr, casrn_chemical, name_crop_earthstat) %>%
  summarize(summass = sum(mass))


input_caschem_country <- input_caschem %>%
  group_by(name_country, casrn_chemical,name_crop_earthstat) %>%
  summarize(summassori = sum(applied_mass_kkg), sumarea = sum(treated_area_kha))

exist.dat.chem <- exist.dat %>%
  #filter(casrn_chemical == chem) %>%
  select(name_crop_earthstat, name_region.y, name_group_yy, HDI, landevap, layer_climate, climate_main, climate_sub, score, logwd, casrn_chemical) %>%
  mutate(group = "ori")
chem_full_xgb_pred <- chem_full_xgb %>%
  #filter(casrn_chemical == chem) %>%
  mutate(logwd = pred.xgb) %>%
  select(name_crop_earthstat, name_region.y, name_group_yy, HDI, landevap, layer_climate, climate_main, climate_sub, score, logwd, casrn_chemical) %>%
  mutate(group = "pred")
chem_dose <- rbind(exist.dat.chem, chem_full_xgb_pred)
for(i in 1:57){
  chem_dose %>%
  filter(casrn_chemical %in% chem.list[(5*i-4):(5*i)]) %>%
  filter(!is.na(name_region.y)) %>%  #check region NA scenarios
  ggplot(aes(x = name_crop_earthstat, y = wd)) +
  geom_boxplot(size = 1,
               outlier.shape = NA,
               #outlier.color = "black",
               #outlier.size = 1,
               aes(fill = group)) +
  geom_jitter(alpha = 0.5, width = 0.2, aes(color = name_region.y), size = 1) +
  theme_minimal() +
  facet_wrap(~ casrn_chemical, scales = "free_x", nrow = 1) +
  #geom_smooth(method=lm, formula = formula, se=FALSE, fullrange=TRUE) +
  scale_color_brewer(palette="Paired")+
  coord_flip()
ggsave(paste0("20220823chem_dose_pred_ori", i, ".jpeg"), width = 40, height = 20, units = "cm")
}
chem_dose %>%
  filter(casrn_chemical %in% chem.list[5]) %>%
  #filter(casrn_chemical == "1071-83-6") %>%
  filter(!is.na(name_region.y)) %>%  #check region NA scenarios
  ggplot(aes(x = name_crop_earthstat, y = wd)) +
  geom_boxplot(size = 1,
               outlier.shape = NA,
               #outlier.color = "black",
               #outlier.size = 1,
               aes(fill = group)) +
  geom_jitter(alpha = 0.5, width = 0.2, aes(color = name_region.y), size = 1) +
  theme_minimal() +
  facet_wrap(~ casrn_chemical, scales = "free_x", nrow = 1) +
  #geom_smooth(method=lm, formula = formula, se=FALSE, fullrange=TRUE) +
  scale_color_brewer(palette="Paired")+
  coord_flip()
ggsave("20220818chem_dose_pred_ori_101007-96-1.jpeg", width = 40, height = 20, units = "cm")
```

```{r}
write.csv(join_short_uni_ratio_r, "20220830join_short_uni_ratio_r.csv")
join_short_uni_ratio_r <- read.csv("20220830join_short_uni_ratio_r.csv")
join_short_uni_ratio_r <- join_short_uni_ratio_r %>%
  #mutate(score = round(as.numeric(score), 13)) %>%
  mutate(name_country = case_when(name_cntr == "The Former Yugoslav Republic O" ~ "Macedonia, the former Yugoslav Republic of",
                                  name_cntr == "Republic Of Korea" ~ "Korea (the Republic of)",
                                  name_cntr == "Iran, (islamic Republic of)" ~ "Iran (Islamic Republic of)",
                                  name_cntr == "United Republic Of Tanzania" ~ "Tanzania, the United Republic of",
                                  name_cntr == "U.k. Of Great Britain And Nort" ~ "United Kingdom",
                                  name_cntr == "United States Of America" ~"United States of America",
                                  name_cntr == "Republic Of Moldova" ~ "Moldova (the Republic of)",
                                  TRUE ~ name_cntr)) 
chem_dose_r <- chem_dose %>%
  mutate(score = round(as.numeric(score),13))
write.csv(chem_dose, "20220920chem_dose.csv")
chem_dose <- read.csv("20220920chem_dose.csv")
write.csv(join_short_uni_ratio_r, "20220920join_short_uni_ratio_r.csv")
join_short_uni_ratio_r <- read.csv("20220920join_short_uni_ratio_r.csv")
country_chemlist_other <- chem_dose %>%
  left_join(join_short_uni_ratio_r, by = c("score", "name_crop_earthstat" = "variable"))


#check dose range
country_pred_chemlist_95 <- country_chemlist_other %>%
  filter(group == "pred") %>%
  group_by(name_country, name_crop_earthstat, casrn_chemical) %>%
  filter(logwd < quantile(country_chemlist_other$logwd, 0.95))
country_chemlist_other %>%
  filter(group == "pred") %>%
  ggplot(aes(x = name_crop_earthstat,y = 10^logwd)) +
  geom_boxplot()+
  theme_bw() +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)))
#check scenarios cannot find country
country_chemlist_other_na <- country_chemlist_other %>%
  filter(is.na(layer_climate.x))

#check country pesticide count
country_chemlist_other_count <- country_chemlist_other %>%
  group_by(name_country, group) %>%
  summarize(predictgroupcount = n_distinct(group), chemicalcount = n_distinct(casrn_chemical), predict = list(unique(group))) %>%
  left_join(no.country.continent, by = c("name_country" = "name_country"))
country_chemlist_other_count %>%
  group_by(name_country) %>%
  summarize(duplicate = n()) %>%
  filter(duplicate > 1)

country_chemlist_other_count %>%
  filter(!is.na(name_country)) %>%
  filter(name_country != "Nigeria") %>%
  filter(!is.na(name_region)) %>%
  ggplot(aes(x = name_country, y = chemicalcount)) +
  geom_bar(aes(fill = group), stat='identity') +
  facet_wrap(~name_region, scales = "free_x") +
  scale_x_discrete(guide = guide_axis(angle = 90))
ggsave("20220920country_chemlist_count.jpeg", width = 12, height = 8)

country_chemlist_other_countcrop <- country_chemlist_other %>%
  group_by(name_country, group, name_group_yy) %>%
  summarize(predictgroupcount = n_distinct(group), chemicalcount = n_distinct(casrn_chemical), predict = list(unique(group))) %>%
  left_join(no.country.continent, by = c("name_country" = "name_country"))

country_chemlist_other_countcrop %>%
  filter(!is.na(name_country)) %>%
  filter(name_country != "Nigeria") %>%
  filter(!is.na(name_region)) %>%
  filter(name_region == "Oceania") %>%
  ggplot(aes(x = name_country, y = chemicalcount)) +
  geom_bar(aes(fill = group), stat='identity') +
  facet_wrap(~name_group_yy) +
  scale_x_discrete(guide = guide_axis(angle = 90))
ggsave("20220920country_chemlist_countnorthoceania.jpeg", width = 60, height = 30, units = "cm")

#check countries predicted nothing
country_chemlist_no <- no.country.continent %>%
  filter(!name_country%in%country_chemlist_other_count$name_country)

croparea_country <- join_short_country_uni_ratio %>%
  group_by(name_cntr) %>%
  summarize(sumcroparea = sum(cropsumarea)) %>%
  mutate(name_country = case_when(name_cntr == "The Former Yugoslav Republic O" ~ "Macedonia, the former Yugoslav Republic of",
                                  name_cntr == "Republic Of Korea" ~ "Korea (the Republic of)",
                                  name_cntr == "Iran, Islamic Republic of" ~ "Iran (Islamic Republic of)",
                                  name_cntr == "United Republic Of Tanzania" ~ "Tanzania, the United Republic of",
                                  name_cntr == "U.k. Of Great Britain And Nort" ~ "United Kingdom",
                                  name_cntr == "United States Of America" ~"United States of America",
                                  name_cntr == "Republic Of Moldova" ~ "Moldova (the Republic of)",
                                  TRUE ~ name_cntr)) %>%
  left_join(no.country.continent, by = c("name_country" = "name_country"))
```

```{r}
no.dat.cpp.pred.exist.full0.05 <- read.csv("C:/me/data gaps/20221020no.dat.cpp.pred.exist.fullsig0.05.csv")
no.dat.cpp0.05 <- no.dat.cpp.pred.exist.full0.05 %>%
  left_join(join_short_uni, by = c("HDI", "landevap", "score", "name_crop_earthstat" = "variable"))

n_distinct(no.dat.cpp0.05$casrn_chemical)

no_cpp_ccc0.05 <- no.dat.cpp0.05 %>%
  group_by(name_cntr, name_crop_earthstat, casrn_chemical) %>%
  summarize(count = n())
no_cpp_cc0.05 <- no.dat.cpp0.05 %>%
  group_by(name_cntr, name_crop_earthstat) %>%
  summarize(countchem = n_distinct(casrn_chemical))
no_cpp_country0.05 <- no.dat.cpp0.05 %>%
  group_by(name_cntr) %>%
  summarize(count0.05 = n_distinct(casrn_chemical))
no_cpp_cc0.05 %>%
  left_join(no.country.continent, by = c("name_cntr" = "name_country")) %>%
  #mutate(countchem = count) %>%
  filter(!is.na(name_region)) %>%
  ggplot(aes(x = countchem)) +
  geom_histogram() +
  facet_wrap(~name_region)

no.dat.cpp.pred.exist.full0.1 <- read.csv("C:/me/data gaps/20221006no.dat.cpp.pred.exist.fullsig0.1.csv")
no.dat.cpp0.1 <- no.dat.cpp.pred.exist.full0.1 %>%
  left_join(join_short_uni, by = c("HDI", "landevap", "score", "name_crop_earthstat" = "variable"))

n_distinct(no.dat.cpp0.1$casrn_chemical)

no_cpp_ccc0.1 <- no.dat.cpp0.1 %>%
  group_by(name_cntr, name_crop_earthstat, casrn_chemical) %>%
  summarize(count = n())
no_cpp_cc0.1 <- no.dat.cpp0.1 %>%
  group_by(name_cntr, name_crop_earthstat) %>%
  summarize(countchem = n_distinct(casrn_chemical))
no_cpp_country0.1 <- no.dat.cpp0.1 %>%
  group_by(name_cntr) %>%
  summarize(count0.1 = n_distinct(casrn_chemical))
no_cpp_cc0.1 %>%
  ggplot(aes(x = countchem)) +
  geom_histogram()


no.dat.cpp.pred.exist.full0.15 <- read.csv("C:/me/data gaps/20221006no.dat.cpp.pred.exist.fullsig0.15.csv")
no.dat.cpp0.15 <- no.dat.cpp.pred.exist.full0.15 %>%
  left_join(join_short_uni, by = c("HDI", "landevap", "score", "name_crop_earthstat" = "variable"))

n_distinct(no.dat.cpp0.15$casrn_chemical)

no_cpp_ccc0.15 <- no.dat.cpp0.15 %>%
  group_by(name_country, name_crop_earthstat, casrn_chemical) %>%
  summarize(count = n())

no_cpp_country0.15 <- no.dat.cpp0.15 %>%
  group_by(name_country) %>%
  summarize(count0.15 = n_distinct(casrn_chemical))

no.dat.cpp.pred.exist.full0.2 <- read.csv("C:/me/data gaps/20221006no.dat.cpp.pred.exist.fullsig0.2.csv")
no.dat.cpp0.2 <- no.dat.cpp.pred.exist.full0.2 %>%
  left_join(join_short_uni, by = c("HDI", "landevap", "score", "name_crop_earthstat" = "variable"))

no.dat.cpp0.2_luxemborg <- no.dat.cpp0.2 %>%
  filter(name_country == "Luxembourg") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())

n_distinct(no.dat.cpp0.2$casrn_chemical)

no_cpp_ccc0.2 <- no.dat.cpp0.2 %>%
  group_by(name_country, name_crop_earthstat, casrn_chemical) %>%
  summarize(count = n())
no_cpp_country0.2 <- no.dat.cpp0.2 %>%
  group_by(name_country) %>%
  summarize(count0.2 = n_distinct(casrn_chemical))
no_cpp_country <- no_cpp_country0.2 %>%
  left_join(no_cpp_country0.15, by = c("name_country")) %>%
  left_join(no_cpp_country0.1, by = c("name_country")) %>%
  left_join(no_cpp_country0.05, by = c("name_country"))
write.csv(no_cpp_country, "20221006no_cpp_country.csv")
exist_country <- exist.dat %>%
  group_by(name_country, name_crop_earthstat) %>%
  #group_by(name_country) %>%
  summarize(count = n_distinct(casrn_chemical)) %>%
  mutate(source = "ori")
country_count <- no_cpp_country0.05 %>%
  mutate(count = count0.05) %>%
  select(name_cntr, count) %>%
  mutate(name_country = name_cntr) %>%
  select(name_country, count) %>%
  mutate(source = "pred")
country_count <- rbind(exist_country, country_count)
country_Count <- country_count %>%
  left_join(no.country.continent, by = c("name_country"))
country_Count %>%
  filter(!is.na(name_country)) %>%
  ggplot(aes(x = name_country, y = count, fill = source)) +
  geom_bar(stat='identity') +
  facet_wrap(~name_region, scales = "free_x") +
  scale_x_discrete(guide = guide_axis(angle = 90))
ggsave("20221027sig0.05countrychemcount6.jpeg", width = 30, height = 20, units = "cm")

nocountryprediction <- country_croparea %>%
  filter(!name_country %in% country_count$name_country) %>%
  group_by(name_country, sumcroparea) %>%
  summarize(sum = sum(croparea))
```


```{r}
#countries cannot be predicted
country_noprediction <- no.dat %>%
  group_by(name_country) %>%
  summarize(countcrop = n_distinct(variable)) %>%
  filter(!name_country %in% no_cpp_country0.05$name_cntr) %>%
  left_join(country_croparea, by = c("name_country" ))
```


#Luxembourg
```{r}
#no.dat.cpp0.05 <- read.csv("C:/me/data gaps/20221004dat.out.cpp0.1.csv")
no.dat.cpp0.05_luxemborg <- no.dat.cpp0.05 %>%
  filter(name_country == "Luxembourg") %>%
  #filter(!casrn_chemical %in% regu_luxembourg$`CAS number`) %>%
  #filter(!casrn_chemical %in% pan_eu$`CAS No`) %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())
eurostat_luxembourg <- read_xlsx("C:/me/Database/harmonization/chemical_eurostat_luxembourg.xlsx")

eurostat_luxembourg <- eurostat_luxembourg %>%
  rowwise() %>%
  mutate(sum = sum(`1516` , `1617` , `1718` , `1314` , `1415`, na.rm = TRUE)) %>%
  filter(sum !=0) %>%
  filter(!is.na(`1718`)) %>%
  filter(!is.na(chemical_casrn))
luxembourg_euro_pred <- eurostat_luxembourg %>%
  full_join(no.dat.cpp0.05_luxemborg, by = c("chemical_casrn" = "casrn_chemical"))
luxembourg_all <- luxembourg_euro_pred %>%
  filter(!is.na(count) & ! is.na(code_eurostat)) %>%
  mutate(indication = str_sub(code_eurostat, 1, 1))
luxembourg_all %>%
  ggplot(aes(x = indication)) +
  geom_histogram(stat = "count")

regulation <- read_xlsx("C:/me/map/regulations/PIC (version 1).xlsx")
pan <- read_xlsx("C:/me/map/regulations/pan_bans.xlsx")
pan_eu <- pan %>%
  select(`CAS No`, EU) %>%
  filter(!is.na(EU))
regu_luxembourg <- regulation %>%
  filter(Country == "Luxembourg")
euro_luxembourg <- eurostat_luxembourg %>%
  group_by(chemical_casrn, code_eurostat) %>%
  summarize(count = n()) %>%
  filter(!chemical_casrn %in% regu_luxembourg$`CAS number`) %>% 
  #filter(chemical_casrn %in% chem.list) %>%
  filter(!chemical_casrn %in% pan_eu$`CAS No`) %>%
  mutate(indication = str_sub(code_eurostat, 1, 1))
euro_luxembourg %>%
  ggplot(aes(x = indication)) +
  geom_histogram(stat = "count")
unique(euro_luxembourg$code_eurostat)

```

#usa chem vs. usgs
```{r}
usgs_chem <- read_xlsx("C:/me/Database/harmonization/usgs_cas.xlsx")
usa_chem <- input_caschem %>%
  filter(name_country == "United States of America") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())
usgs_chem <- usgs_chem %>% 
  filter(!is.na(casrn_chemical))

usa_chem_all <- usa_chem %>%
  full_join(usgs_chem, by = c("casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(casrn_chemical.x)) %>%
  filter(!is.na(casrn_chemical.y))
```

#Denmark chem vs. eurostat
```{r}
denmark_chem <- read_xlsx("C:/me/comparison/Denmark.xlsx")
denmark_chem2017 <- denmark_chem %>%
  filter(`2017` != "A") %>%
  filter(`2017` != "B") %>%
  filter(!is.na(`2017`)) %>%
  filter(`2017` != "0,0")
denmark_agro <- input_caschem %>%
  filter(name_country == "Denmark") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())
denmark_chemall <- denmark_chem2017 %>%
  full_join(denmark_agro, by = c("CAS-nr." = "casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(casrn_chemical)) %>%
  filter(!is.na(`CAS-nr.`))
```


#Czechia chem vs. national
```{r}
eurostat_code_cas <- read_xlsx("C:/me/comparison/eurostat_code_cas.xlsx")
czechia_chem2017 <- read_xlsx("C:/me/comparison/Czechia_2017.xlsx", sheet = 2)
czechia_chemcode <- read_xlsx("C:/me/comparison/Czechia_2017.xlsx", sheet = 1)
czechia_chem2017 <- czechia_chem2017 %>%
  left_join(czechia_chemcode, by = c("active" = "Column1")) %>%
  filter(!is.na(Column2))
unique(czechia_chem2017$Column3)
czechia_chem2017_cas <- czechia_chem2017 %>%
  left_join(eurostat_code_cas, by = c("Column3" = "C1")) %>%
  select(active, total, Column3, C4)
write.csv(czechia_chem2017_cas, "C:/me/comparison/czechia_chem2017_cas.csv")

czechia_chem2017_cas <- read_xlsx("C:/me/comparison/czechia_chem2017_cas.xlsx", sheet = 1)
czechia_chem2017_cas_regu <- czechia_chem2017_cas %>%
  filter(!C4 %in% regu_luxembourg$`CAS number`) %>% 
  #filter(chemical_casrn %in% chem.list) %>%
  filter(!C4 %in% pan_eu$`CAS No`)
unique(czechia_chem2017_cas$Column3)

czechia_agro <- input_caschem %>%
  filter(name_country == "Czech Republic") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n()) %>%
  filter(casrn_chemical %in% regu_luxembourg$`CAS number`) %>% 
  #filter(chemical_casrn %in% chem.list) %>%
  filter(casrn_chemical %in% pan_eu$`CAS No`)
czechia_chemall <- czechia_chem2017_cas_regu %>%
  full_join(czechia_agro, by = c("C4" = "casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(casrn_chemical)) %>%
  filter(!is.na(C4))
```

#Togo
```{r}
no.dat.cpp0.05_Togo <- no.dat.cpp0.05 %>%
  filter(name_country == "Togo") %>%
  filter(name_crop_earthstat == "vegetablenes") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())
exist.dat_ivory <- exist.dat %>%
  filter(name_country == "Ivory Coast") %>%
  filter(name_crop_earthstat == "vegetablenes") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())
exist.dat_ghana <- exist.dat %>%
  filter(name_country == "Ghana") %>%
  filter(name_crop_earthstat == "vegetablenes") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())
exist.dat_southafrica <- exist.dat %>%
  filter(name_country == "South Africa") %>%
  filter(name_crop_earthstat == "vegetablenes") %>%
  group_by(casrn_chemical) %>%
  summarize(count = n())


togo_ivory_veg <- exist.dat_ivory %>%
  full_join(no.dat.cpp0.05_Togo, by = c("casrn_chemical" = "casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(count.x)) %>%
  filter(!is.na(count.y))
togo_ghana_veg <- exist.dat_ghana %>%
  full_join(no.dat.cpp0.05_Togo, by = c("casrn_chemical" = "casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(count.x)) %>%
  filter(!is.na(count.y))
togo_southafrica_veg <- exist.dat_southafrica %>%
  full_join(no.dat.cpp0.05_Togo, by = c("casrn_chemical" = "casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(count.x)) %>%
  filter(!is.na(count.y))
ivory_ghana_veg <- exist.dat_ivory %>%
  full_join(exist.dat_ghana, by = c("casrn_chemical" = "casrn_chemical"), keep = TRUE) %>%
  filter(!is.na(count.x)) %>%
  filter(!is.na(count.y))

country_croparea_ratio <- country_croparea %>%
  mutate(ratio = croparea/sumcroparea * 100)
```

```{r}
input_caschem_vietnam <- input_caschem %>%
  filter(name_country == "Viet Nam") %>%
  group_by(name_country, name_crop_earthstat, casrn_chemical, name_activeindication, name_ai) %>%
  summarize(summass = sum(applied_mass_kkg))


mass <- input_caschem %>%
  group_by(name_country) %>%
  summarize(mass = sum(applied_mass_kkg), area = sum(treated_area_kha))
```

